---
title: "Lecture1Exercise"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

##Exercise 1 - Babynames

First import the necessary libraries for the exercise
```{r}
library(babynames)
library(ggplot2)
library(magrittr)
library(dplyr)
```

A look at the data
```{r}
str(babynames)
```

From the top
```{r}
head(babynames)
```

To the bottom
```{r}
tail(babynames)
```

The number of names are:
```{r}
length(unique(babynames$name))
```

How many kids are there total?
```{r}
sum(babynames$n)
```

Plot a single name over time
```{r}
ggplot(babynames, aes(year,n)) + geom_line(data=filter(babynames, name == 'Emma'))
```

The above graph is inaccurate. This is shown in the bottom table because the data is for males and females.
```{r}
head(filter(babynames, name == 'Emma'))
```

A graph of the data sorted by sex.
```{r}
ggplot(babynames, aes(year,n)) + geom_line(data=filter(babynames, name == 'Emma'), aes(color = sex))
```

Top 10 Names over time
```{r}
top_ten <- babynames %>%
  group_by(sex, name) %>%
  summarize(total = sum(n)) %>%
  arrange(desc(total)) %>%
  group_by(sex) %>%
  mutate(rank=row_number()) %>%
  filter(rank <= 10) %>%
  arrange(sex, rank)

top10_f <- top_ten %>% filter(sex=='F')
top10_m <- top_ten %>% filter(sex == 'M')
```

Girls
```{r}
top10_f
```

Boys
```{r}
top10_m
```

Plot of Top 10 most common names
```{r}
babynames %>%
  filter(sex=='F')%>%
  filter(name %in% top10_f$name) %>%
  ggplot(., aes(year, n)) + geom_line(aes(color=name, group=name))
```

```{r}
babynames %>%
  filter(sex=='M')%>%
  filter(name%in% top10_m$name) %>%
  ggplot(., aes(year, n)) + geom_line(aes(color=name, group=name))
```

Top 10 Names of 2013
```{r}
top_10_2013 <- babynames %>%
  filter(year == 2013) %>%
  group_by(sex, name, year) %>%
  summarize(total_2013 = sum(n)) %>%
  arrange(desc(total_2013)) %>%
  group_by(sex) %>%
  mutate(rank=row_number()) %>%
  filter(rank <= 10) %>%
  arrange(sex, rank, year)

top_10_2013_f <- top_10_2013 %>% filter(sex == 'F')
top_10_2013_m <- top_10_2013 %>% filter(sex == 'M')
```

Plot of top 10 Names of 2013
```{r}
babynames %>% 
  filter(sex == 'F') %>%
  filter(name %in% top_10_2013_f$name) %>%
  ggplot(., aes(year, n)) + geom_line(aes(color=name, group=name))
```

```{r}
babynames %>%
  filter(sex == 'M') %>%
  filter(name %in% top_10_2013_m$name) %>%
  ggplot(., aes(year, n)) + geom_line(aes(color=name, group=name))
```

Unisex Names
```{r}

```



